Dynamic Transition Analysis with TIMES

### 2019-01-12 doc/2019-01-poster/poster.tex
updated poster, added new data
Former-commit-id: 58ff1cab0f45228c427b60b60ca011f0636f7a36 [formerly 4f2bf9a0b4c76fe6832c739e19ce11de67b30fa9]
Former-commit-id: 9671cbfeff916ede3f4ea25d12f298abbbffbd81

\begin{description}
{\large 
        \item[\textbf{Division:}] Energy Analysis Division
        \item[\textbf{Project:}] I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions
        \item[\textbf{Objective:}] Evaluate potential impact of novel energy technologies within Japan's energy system.
\item[\textbf{Milestones:}] ~\\}
        \begin{itemize}
        \item Minimize carbon emissions within realistic constraints.
        \item Optimize realistic 2010-2050 decarbonization roadmaps.
	\item Identify high impact technologies.
        \item Identify potential transition bottlenecks.
        \item Help Japan's policymakers create timelines for R\&D investment and infrastructure development.
        \item Quantify system sensitivity to technology readiness.
	\item Predict impediments to strategically optimal technology deployment.
	\end{itemize}
\end{description}

@@

         \item Hydropower capacity held constant \cite{noauthor_energy_2018}.

         \item The cost of fossil fuels, geothermal, hydropower, steam reforming and nuclear is held constant. Variation in costs of wind, solar, and photocatalytic H$_2$ production is given in Fig. \ref{cost}.

@@

%--------------------------------------------------------
% PROJECT TIMELINE
%---------------------------------------------------------
\begin{block}{Future work}
    \begin{itemize}

    \item Capture realistic, gradual transition behaviour.

@@

\vspace{10mm}
\begin{center}
\begin{tabular}{cccc}
\includegraphics[scale=0.5]{arfc_logo.png} & \includegraphics[scale=0.5]{wpi_logo.png} & \includegraphics[scale=0.1]{ku_logo.png} &\includegraphics[scale=0.7]{i2cner_logo.png}
%\includegraphics[width=\linewidth, height=0.1\textheight]{i2cner_logo.png}
\end{tabular}
\end{center}

>>>>

\begin{description}
{\large 
        \item[\textbf{Division:}] Energy Analysis Division
        \item[\textbf{Project:}] I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions
        \item[\textbf{Objective:}] Evaluate potential impact of novel energy technologies within Japan's energy system.
\item[\textbf{Milestones:}] ~\\}
        \begin{itemize}
        \item Minimize carbon emissions within realistic constraints.
        \item Optimize realistic 2010-2100 decarbonization roadmaps.
	\item Identify high impact technologies.
        \item Identify potential transition bottlenecks.
        \item Help Japan's policymakers create timelines for R\&D investment and infrastructure development.
        \item Quantify system sensitivity to technology readiness.
	\item Predict impediments to strategically optimal technology deployment.
	\end{itemize}
\end{description}

@@

         \item Hydropower and geothermal capacity held constant \cite{noauthor_energy_2018}.

         \item Variation in costs of wind, solar, and photocatalytic H$_2$ production is given in Fig. \ref{cost}.

@@

%--------------------------------------------------------
% PROJECT TIMELINE
%---------------------------------------------------------
\begin{block}{Limitations and Future work}
    \begin{itemize}

    \item Model focuses entirely on \textbf{electricity supply sector}.

    \item The cost of fossil fuels, geothermal, hydropower, steam reforming and nuclear is held constant.

    \item No limit on penetration of solar or wind except maximum potential.

    \item Annual timestep does not capture seasonal and daily variation in wind and solar.

    \item Capture realistic, gradual transition behaviour and fluctuations in demand.

@@

%\vspace{10mm}
\begin{center}
\begin{tabular}{cccc}
\includegraphics[scale=0.5]{arfc_logo.png} & \includegraphics[scale=0.5]{wpi_logo.png} & \includegraphics[scale=0.1]{ku_logo.png} &\includegraphics[scale=0.7]{i2cner_logo.png}
%\includegraphics[width=\linewidth, height=0.1\textheight]{i2cner_logo.png}
\end{tabular}
\end{center}
